{\large Master Thesis}\\{\normalsize on

### 2011-07-20 doc/report.tex
m

% TODOs
% skarpere plots
% hav plot for $r=\sqrt n$ med til forsvar

@@

The algorithm keeps the invariant $\zlabel(p_i[0\twodots v]) = \zlabel(p_j[0\twodots v])$. At each iteration we find $v'$, which is the longest common prefix of $\zlabel(p_i[v\twodots v+m_i])$ and $\zlabel(p_j[v\twodots v+m_j])$. This gives $\zlabel(p_i[0\twodots v+v']) = \zlabel(p_j[0\twodots v+v'])$, and we therefore keep the invariant when we add $v'$ to $v$ in step five.

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.4\textwidth,page=1]{ladder.pdf}
        \includegraphics[width=0.4\textwidth,page=2]{ladder.pdf}
    \end{center}
    \caption{\label{fig:ladder-ds} Ladders of a tree before and after their length is doubled. A \proc{LadderLce} string $s$ for this ladder decomposition is $s=abc|ade|df|ghijkl|ghno|jm$, where the splits between ladders are marked with a vertical line.}
\end{figure}

@@

\begin{lemma}
The \proc{LadderLce} query finds the correct LCE value.
\end{lemma}
\begin{proof}
In step two, $\zlength(p_i[v\twodots v+m_i]) +1 \leq \zlength(p_i[v+m_i\twodots e_i])\leq h(p_i[v+m_i])$, where $h$ is the height of a node. For a node $u$ of height $h$, the ladder decomposition guarantees that $u$'s ancestor with distance $h+1$ to $u$ is in $u$'s ladder. Therefore, $p_i[v+1]$ is in $p_i[v+m_i]$'s ladder, and $s[i\twodots i+m_i-1] = \zlabel(p_i[v\twodots v+m_i])$. Similarly in step three, $s[j\twodots j+m_i-1] = \zlabel(p_j[v\twodots v+m_j])$.

>>>>

% TODOs
% skarpere plots
% sørg for at figurer ikke sidder underligt
% Prøv at formindske for store mellemrum mellem ord ved at lave påtvungne linjeskift
% hav plot for $r=\sqrt n$ med til forsvar

@@

The algorithm keeps the invariant $\zlabel(p_i[0\twodots v]) = \zlabel(p_j[0\twodots v])$. At each iteration we find $v'$, which is the length of the longest common prefix of $\zlabel(p_i[v\twodots v+m_i])$ and $\zlabel(p_j[v\twodots v+m_j])$. This gives $\zlabel(p_i[0\twodots v+v']) = \zlabel(p_j[0\twodots v+v'])$, and we therefore keep the invariant when we add $v'$ to $v$ in step five.

@@

\begin{figure}[tp]
    \begin{center}
        \includegraphics[width=0.4\textwidth,page=1]{ladder.pdf}
        \includegraphics[width=0.4\textwidth,page=2]{ladder.pdf}
    \end{center}
    \caption{\label{fig:ladder-ds} Ladders of a tree before and after their size is doubled. A \proc{LadderLce} string $s$ for this ladder decomposition is $s=abc|ade|df|ghijkl|ghno|jm$, where the splits between ladders are marked with a vertical line.}
\end{figure}

@@

\begin{lemma}
The \proc{LadderLce} query finds the correct LCE value.
\end{lemma}
\begin{proof}
In step two, $\zlength(p_i[v\twodots v+m_i]) +1 \leq \zlength(p_i[v+m_i\twodots e_i])\leq h(p_i[v+m_i])$, where $h(u)$ is the height of node $u$. For a node $u$ of height $h$, the ladder decomposition guarantees that $u$'s ancestor with distance $h+1$ to $u$ is in $u$'s ladder. Therefore, $p_i[v+1]$ is in $p_i[v+m_i]$'s ladder, and $s[i\twodots i+m_i-1] = \zlabel(p_i[v\twodots v+m_i])$. Similarly in step three, $s[j\twodots j+m_i-1]\\ = \zlabel(p_j[v\twodots v+m_j])$.
